### 2019-03-21 5_evaluation.tex
More text for evaluation section.

>>>>

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under varying amounts of load imbalance. The
imbalanced workloads are generated by randomly varying the task
durations according by a factor determined by the formula $1+(X-0.5)I$
where $X$ is a uniform random variable in the range $[0,1]$ and $I$ is
the degree of imbalance in the range $[0,2]$. The random numbers are
generated with a deterministic pseudo random number generator with a
deterministic seed to ensure that the task durations under all systems
are identical.

The MPI implementation of Task Bench, being bulk synchronous,
obviously suffers the most under load imbalance. The biggest
difference is at large task granularities, where the imbalance has the
effect of putting an upper bound on MPI efficiency. At smaller task
granularities the effect shrinks and may even reverse as systems hit
their fundamental limits due to overhead.

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. For example, OpenMP
executes tasks via a thread pool, resulting in a form of work
stealing. This on-node work stealing, in combination with the task
parallelism due to the presence of 4 task graphs, is sufficient to
completely mitigate load imbalance. Systems which exploit task
parallelism but not work stealing on a node achieve lower peak
efficiency, but may achieve smaller task granularities as a result of
not relying on a shared global queue for tasks.
